Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-04-11 paper.qmd
added lims for last plot

trimesh_removed_scurve <- vis_rmlg_mesh(distance_edges = distance_scurve, 
                                        benchmark_value = benchmark_scurve, 
                                        tr_coord_df = tr_from_to_df_scurve, 
                                        distance_col = "distance") +
  interior_annotation_left("d") 
```

>>>>

trimesh_removed_scurve <- vis_rmlg_mesh(distance_edges = distance_scurve, 
                                        benchmark_value = benchmark_scurve, 
                                        tr_coord_df = tr_from_to_df_scurve, 
                                        distance_col = "distance") +
  xlim(c(-0.3, 1.3)) + ylim(c(-0.3, 2.6)) +
  interior_annotation_left("d") 
```
